Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-02-16 AO_bondedSi.tex
MGS edits down to the end of the paper

\begin{abstract}
Silicon direct bonding offers flexibility in the design and development of Si optics by allowing manufacturers to combine subcomponents with a potentially lossless and mechanically stable interface. The bonding process presents challenges in meeting the requirements for optical performance because air gaps at the Si interface cause large Fresnel reflections. Even small (35 nm) gaps reduce transmission through a direct bonded Si compound optic by 4\% at $\lambda = 1.25 \; \mu$m at normal incidence. Understanding the optical effects of such gaps and evaluation of various methods for preventing or eliminating them demands that we have a method for measuring not only the two-dimensional extent of the gaps but also their axial extent.  Existing methods for studying gaps provide only poor measures of this axial extent.  We describe a bond inspection method that makes use of precision transmission spectroscopy.  Using spectroscopy, we can detect and measure gaps as small as 12 nm by measuring transmission as a function of wavelength. Our approach involves modeling multiple incoherent reflections within the substrate interfaces with a wave transfer matrix, modified for intensities rather than complex amplitudes. We infer the gap axial extent and fill factor with Monte Carlo Markov Chain (MCMC) and a flexible Gaussian process noise model.  We describe the measurement and analysis techniques and demonstrate the validity of the approach by measuring bond gaps of known depths produced by microlithography.
\end{abstract}

@@

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
              \includegraphics[width=\textwidth]{figs/VG02p3_corner.pdf}
              \caption{Fitted gap size $d$ and fill factor $f$ for VG02}
		\label{fig_VG02p3_corner}
        \end{subfigure}

@@

\emph{Origin and properties of correlated noise- } Another key assumption of the model is that correlated errors dominate the measurement uncertainty.  This is the same thing as saying that there is an instrumental bias, or that our measurements are \emph{precise} but \emph{inaccurate}.  The extent to which the measurement is inaccurate is tabulated in \ref{tbl_cary5000Pars}, as already mentioned.  We have assumed that the Gaussian Process model can capture the effect of the observed correlated errors.  But to what extent does the Gaussian Process emulate the \emph{True} covariance matrix, which is unknown?  One way to gauge the goodness of fit of the covariance matrix is to generate synthetic data from a best-fit model.  Many of these synthetic draws are shown in the spectra in Figures \verb|\ref{a thru f}| as transparent blue lines.  When overplotted these lines look like a halo of uncertainty enveloping the model and measurement.  The bulk agreement is encouraging.  We also scrutinized individual synthethic spectra with the measured data, and found that the noise model tended to under-predict the length scale of the correlation.  For example, we typically derive $0.15<a<0.4\%$ and $20<s<200$.  The measured data appear to prefer larger values of $s$.  The discrepancy probably comes from the fact that, in reality, the \emph{True} covariance matrix probably has local structures that cannot be replicated by a simple 2-parameter (\emph{i.e.} $a$ and $s$) estimate of the covariance matrix.  A model employing local covariance structures \verb|\cite{Czekala et al. in press}| could better capture some of the residual structure, but would introduce additional computational complexity with little gain.  Overall the Gaussian Process technique provides much better agreement than the na\"{i}ve assumption of zero correlated errors.

\emph{Validating the MCMC with synthetic data, and addressing heteroscedasticity-}  To evaluate our MCMC fitting method and assumption of homoscedasticity, we generated synthetic data with a known parameters, $d$, $f$, $a$, and $s$ and $\sigma_i$.  We then fit the parameters $d$, $f$, $a$, and $s$ assuming homoscedastic errors, ($\sigma_i = \sigma = 0.02\%$).  The derived physical parameters were consistent with the \emph{Truth} to within the $1\;\sigma$ confidence interval, but we significantly underestimated $s$ (8 nm instead of 200 nm) and marginally underestimated $a$ (0.0013 instead of 0.0016).  This result is reassuring for our estimation of physical parameters, and shows that the Gaussian Process technique captures realistic uncertainty in the physical parameters, despite an imperfect characterization of the noise correlation length.

\emph{Polarization and lamp jumps- } As mentioned, the Cary 5000 double beam mode offers considerably lower amplitude of correlated errors than single beam mode \ref{tbl_cary5000Pars}.  However, the double beam mode was found to have enhanced artifacts at wavelengths at which the Cary 5000 monochromator changes its diffraction grating and light sources.  The sharp jumps in transmission were up to a few percent.  The origin of these jumps could be polarization-dependent transmission losses.  Whatever the origin, they cause large systematic errors.  These are still captured by the Gaussian Process structure.

@@

\emph{Refactive index- } We have assumed that the refractive index is identical to that given by \cite{2006SPIE.6273E..77F}.  Double beam mode measurements can reach a precision of comparable to the part-to-part variation of refractive index.  We have normalized spectra by their singleton counterparts from the same heritage (i.e. same wafer box).

\emph{Diffraction from mesh patterns}
It's conceivable that the mesh patterns Figure \ref{figVS20pattern}.  We ruled out wavelength-dependent diffraction from the mesh pattern as a measurement artifact, since the beam size is large and the angular spread of diffraction from the mesh pattern would be much smaller than the spread of the beam.  To eliminate this concern, we measured in the coarse mesh rather than the medium or fine meshes, when possible.  We saw no difference in the bond quality surrounding the medium or fine meshes, which is consistent with results from the literature \cite{1992JEMat..21..669M}.  Specifically, the gas pressure of bonded wafers grows as the fill factor of gaps decreased.  In other words, what matters is the fill factor of gaps, not their relative sizes.  Since the fine, medium, and coarse meshes had the same fill factors, we anticipate no difference in the pressure of the gaps, and therefore no difference in the bonding properties.

\subsection{What is the smallest gap size this technique can measure?}
In this section we quantify the limits of how far the technique can be pushed.  There are three key ideas when trying to answer the question ``What is the smallest gap size this technique can measure?''.  The answer for single beam mode is evidently $\sim20 nm$ (Figure \ref{fig_VG02p3_corner}).  In principle this number could be pushed down by averaging many spectra, all normalized by different reference spectra.  Alternatively, double beam mode could be used.  The grating jumps noted above would also limit double beam mode analysis.  If these could be rectified, a very low uncertainty would be obtained, and it is conceivable that gaps as small as a few nanometers could be inferred.

@@

The technique and formalism we describe here can detect and measure the axial extent of gaps in Si$-$Si optical bonds down to a level of $20-30\;$nm.  It makes use of widely available off-the-shelf metrology equipment and simple to implement analysis.  Armed with this technique, optical fabricators have a new diagnostic tool to assess the quality of Si$-$Si bonds.

>>>>

\begin{abstract}
Silicon direct bonding offers flexibility in the design and development of Si optics by allowing manufacturers to combine subcomponents with a potentially lossless and mechanically stable interface. The bonding process presents challenges in meeting the requirements for optical performance because air gaps at the Si interface cause large Fresnel reflections. Even small (35 nm) gaps reduce transmission through a direct bonded Si compound optic by 4\% at $\lambda = 1.25 \; \mu$m at normal incidence. Understanding the optical effects of such gaps and evaluation of various methods for preventing or eliminating them demands that we have a method for measuring not only the two-dimensional extent of the gaps but also their axial extent.  Existing methods for studying gaps provide only poor measures of this axial extent.  We describe a bond inspection method that makes use of precision transmission spectroscopy.  Using spectroscopy, we can detect and measure gaps as small as 14 nm by measuring transmission as a function of wavelength. Our approach involves modeling multiple incoherent reflections within the substrate interfaces with a wave transfer matrix, modified for intensities rather than complex amplitudes. We infer the gap axial extent and fill factor with Monte Carlo Markov Chain (MCMC) and a flexible Gaussian process noise model.  We describe the measurement and analysis techniques and demonstrate the validity of the approach by measuring bond gaps of known depths produced by microlithography.
\end{abstract}

@@

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
              \includegraphics[width=\textwidth]{figs/VG02p3_corner.pdf}
              \caption{Fitted gap size $d$ and fill factor $f$ for VG09-12 off-mesh}
		\label{fig_VG02p3_corner}
        \end{subfigure}

@@

\emph{Origin and properties of correlated noise- } Another key assumption of the model is that correlated errors dominate the measurement uncertainty.  We have assumed that the Gaussian Process can capture the effect of the observed correlated errors.  We tested the need for Gaussian process regression by generating synthetic data spectra with known gap size and fill factor, and known covariance structure.  We applied ordinary least squares regression to the synthetic spectra and derived values for $d$ and $f$ that were biased by up to $20\sigma$ or more.  Applying Gaussian process regression recovered the input values to within $1\sigma$.

@@

\emph{Refactive index- } We have assumed that the refractive index is identical to that given by \cite{2006SPIE.6273E..77F}.  Double beam mode measurements can reach a precision of comparable to the part-to-part variation of refractive index.  We have attempted to normalize spectra by their singleton counterparts when possible.  We do not present measurements made with double beam mode in this article.

\emph{Diffraction from mesh patterns}
It's conceivable that the edges of the mesh patterns diffract or scatter the beam (Figure \ref{figVS20pattern}).  We ruled out wavelength-dependent diffraction from the mesh pattern as a measurement artifact, since the beam size is large and the angular spread of diffraction from the mesh pattern would be much smaller than the spread of the beam.  To eliminate this concern, we measured in the coarse mesh rather than the medium or fine meshes, when possible.  We saw no difference in the bond quality surrounding the medium or fine meshes, which is consistent with results from the literature \cite{1992JEMat..21..669M}.  Specifically, the gas pressure of bonded wafers grows as the fill factor of gaps decreased.  In other words, what matters is the fill factor of gaps, not their relative sizes.  Since the fine, medium, and coarse meshes had the same fill factors, we anticipate no difference in the pressure of the gaps, and therefore no difference in the bonding properties.

@@

The technique and formalism we describe here can detect and measure the axial extent of gaps in Si$-$Si optical bonds down to a level of $\sim14\;$nm.  It makes use of widely available off-the-shelf metrology equipment and simple to implement analysis.  Armed with this technique, optical fabricators have a new diagnostic tool to assess the quality of Si$-$Si bonds.
